\frb: Multi-Telescope Burst Properties and Implications for FRB Population

### 2016-12-10 repeater-vladata.tex
adding notes on naming, simulations.

@@

Simulate cosmic volume uniformly filled with \frb...

@@

>>>>

\frb\ is detectable with the VLA out to $z=0.7$ and much farther with Arecibo...

@@

Simulate cosmic volume uniformly filled with \frb... Also once done with a theoretical model based on young pulsars \citep{2016MNRAS.462..941L}

Scaling up assumes that this source is representative. Propagation effects may amplify or alter burst brightness statistical properties. Some such effects are possible near the burst source (e.g., Jim's caustic analysis), which would effectively be intrinsid in this context.

@@

\subsection{Naming Convention}

The cosmological distance for \frb\ and consistency with the overall population suggests that most FRBs repeat. The current naming convention for FRBs is analogous to supernovae, with six numbers defining the year, month, and day of detection. If all FRBs repeat, then this naming convention is only useful for identifying its discovery. A more useful convention would be the more common one that uses the coordinates. But there are already two FRBs that have consistent celestial positions and different DMs.

We suggest a convention of referring to FRBs as Jhhmm+dd or appending DM...
